Download, Compile and Link OpenBLAS Library with R

### 2020-12-10 README.Rmd
Update README.md file.

---
title: "Download, Compile and Link OpenBLAS Library with R"
author: |
  | **Author**: Prof. Dr. Pedro Rafael Diniz Marinho
  | **Package website**: **<https://prdm0.github.io/ropenblas>**
  |
  |
  |
  | **Summary**
output: 
  bookdown::github_document2:
    toc: true
toccolor: 'blue'
---

>>>>

---
title: "Download, Compile and Link OpenBLAS Library with R"
author: |
  | **Author**: Prof. Dr. Pedro Rafael Diniz Marinho
  | **Package website**: **<https://prdm0.github.io/ropenblas>**
  |
  |
  |
  | **Summary**
output: 
  bookdown::github_document2:
    number_sections: true
    toc: true
    toc_depth: 2
toccolor: 'blue'
---
